---
title: "Québec Airbnb"
author: "Boucar LY"
output:
  flexdashboard::flex_dashboard:
    theme: paper
    favicon: img/hotel.png
    source_code: embed
---

```{r setup, include=FALSE}
# prep workspace
library(dplyr)  # tidy data manipulation
library(leaflet)  # interative mapping
library(flexdashboard)  
library(DT)  # interactive tables
library(crosstalk)  # inter-widget interactivity
library(plotly)
library(summarywidget)
library(htmltools)
sch <- read.csv("D:/Promutel assurance/listings.csv")
sch <-sch[which(sch$price<9000),]
sd <- SharedData$new(sch)



valueBoxSummaryWidget <- function (value, caption = NULL, icon = NULL, color = NULL, href = NULL) 
{
    if (!is.null(color) && color %in% c("primary", "info", 
        "success", "warning", "danger")) 
        color <- paste0("bg-", color)
    valueOutput <- tags$span(class = "value-summarywidget-output", `data-caption` = caption, 
        `data-icon` = icon, `data-color` = color, 
        `data-href` = href, value)
    hasPrefix <- function(x, prefix) {
        if (!is.null(x)) 
            grepl(paste0("^", prefix), x)
        else FALSE
    }
    fontAwesome <- hasPrefix(icon, "fa")
    ionicons <- hasPrefix(icon, "ion")
    deps <- flexdashboard:::html_dependencies_fonts(fontAwesome, ionicons)
    if (length(deps) > 0) 
        valueOutput <- attachDependencies(valueOutput, deps)
    valueOutput
}
```



<script>
window.FlexDashboardComponents.push({

  type: 'custom',

  find: function(container) {
    if (container.find('span.value-summarywidget-output').length)
      return container;
    else
      return $();
  },

  flex: function(fillPage) {
    return false;
  },

  layout: function(title, container, element, fillPage) {

    // alias variables
    var chartTitle = title;
    var valueBox = element;

    // add value-box class to container
    container.addClass('value-box');

    // value paragraph
    var value = $('<p class="value"></p>');

    // if we have shiny-text-output then just move it in
    var valueOutputSpan = [];
    var shinyOutput = valueBox.find('.shiny-valuebox-output').detach();
    var summaryOutput = valueBox.find('.summarywidget').detach();
    
    if (shinyOutput.length) {
      valueBox.children().remove();
      shinyOutput.html('&mdash;');
      value.append(shinyOutput);
    }
    
    if (summaryOutput.length) {
      value.append(summaryOutput);
      valueOutputSpan = valueBox.find('span.value-summarywidget-output')
    }

    // caption
    var caption = $('<p class="caption"></p>');
    caption.append(chartTitle);

    // build inner div for value box and add it
    var inner = $('<div class="inner"></div>');
    inner.append(value);
    inner.append(caption);
    valueBox.append(inner);

    // add icon if specified
    var icon = $('<div class="icon"><i></i></div>');
    valueBox.append(icon);
    function setIcon(chartIcon) {
      var iconLib = '';
      var iconSplit = chartIcon.split(' ');
      if (iconSplit.length > 1) {
        iconLib = iconSplit[0];
        chartIcon = iconSplit.slice(1).join(' ');
      } else {
        var components = chartIcon.split('-');
        if (components.length > 1)
          iconLib = components[0];
      }
      icon.children('i').attr('class', iconLib + ' ' + chartIcon);
    }
    var chartIcon = valueBox.attr('data-icon');
    if (chartIcon)
      setIcon(chartIcon);

    // set color based on data-background if necessary
    var dataBackground = valueBox.attr('data-background');
    if (dataBackground)
      valueBox.css('background-color', bgColor);
    else {
      // default to bg-primary if no other background is specified
      if (!valueBox.hasClass('bg-primary') &&
          !valueBox.hasClass('bg-info') &&
          !valueBox.hasClass('bg-warning') &&
          !valueBox.hasClass('bg-success') &&
          !valueBox.hasClass('bg-danger')) {
        valueBox.addClass('bg-primary');
      }
    }

    // handle data attributes in valueOutputSpan
    function handleValueOutput(valueOutput) {

      // caption
      var dataCaption = valueOutput.attr('data-caption');
      if (dataCaption)
        caption.html(dataCaption);

      // icon
      var dataIcon = valueOutput.attr('data-icon');
      if (dataIcon)
        setIcon(dataIcon);

      // color
      var dataColor = valueOutput.attr('data-color');
      if (dataColor) {
        if (dataColor.indexOf('bg-') === 0) {
          valueBox.css('background-color', '');
          if (!valueBox.hasClass(dataColor)) {
             valueBox.removeClass('bg-primary bg-info bg-warning bg-danger bg-success');
             valueBox.addClass(dataColor);
          }
        } else {
          valueBox.removeClass('bg-primary bg-info bg-warning bg-danger bg-success');
          valueBox.css('background-color', dataColor);
        }
      }

      // url
      var dataHref = valueOutput.attr('data-href');
      if (dataHref) {
        valueBox.addClass('linked-value');
        valueBox.off('click.value-box');
        valueBox.on('click.value-box', function(e) {
          window.FlexDashboardUtils.showLinkedValue(dataHref);
        });
      }
    }

    // check for a valueOutputSpan
    if (valueOutputSpan.length > 0) {
      handleValueOutput(valueOutputSpan);
    }

    // if we have a shinyOutput then bind a listener to handle
    // new valueOutputSpan values
    shinyOutput.on('shiny:value',
      function(event) {
        var element = $(event.target);
        setTimeout(function() {
          var valueOutputSpan = element.find('span.value-output');
          if (valueOutputSpan.length > 0)
            handleValueOutput(valueOutputSpan);
        }, 10);
      }
    );
  }
});
</script>


Interactives {data-icon="ion-stats-bars"}
=====================================  

Column {data-width=200}
-------------------------------------

### Filtres

```{r Filtres}
filter_select(
  id = "neighbourhood",
  label = "Quartier",
  sharedData = sd,
  group = ~neighbourhood
)

bscols(
  filter_checkbox(
    id = "room_type",
    label = "Type de chambre",
    sharedData = sd,
    group = ~room_type
  )
)

bscols(
  filter_slider(
    id = "price",
    label = "Prix",
    sharedData = sd,
    column = ~price,
    step = 10,
    round = TRUE,
    sep = "",
    ticks = FALSE
  )
)
bscols(
  filter_slider(
    id = "reviews_per_month",
    label = "Nombre de revues par mois",
    sharedData = sd,
    column = ~reviews_per_month,
    step = 1,
    round = TRUE,
    sep = "",
    ticks = FALSE
  )
)
```


Column {data-width=450}
-------------------------------------
    
### Carte interactive
    
```{r map}
sd %>% 
  leaflet::leaflet() %>%
  leaflet::addProviderTiles(providers$OpenStreetMap) %>% 
  leaflet::addAwesomeMarkers(
    popup = ~paste0(
      "<b>Name: </b>", sch$name, "<br>",
      
      "<b>Host Name: </b>", sch$host_name, "<br>",
      
      "<b>Quartier: </b>", sch$neighbourhood, "<br>",
      "<b>Prix: </b>", sch$price, "<br>",
      "<b>Nombre de Reviews: </b>",sch$number_of_reviews, "<br>",
      "",
      
      "",
      "",
      "",
      "",
      "",
      
      "",
      "",
      "",
      "",
      "",
      
      "",
      "",
      "",
      "",
      "",
      
      "",
      "",
      "",
      "",
      ""
    ),  # end popup()
    icon = awesomeIcons(
      library = "ion",
      icon = "ion-android-home" ,
      iconColor = "white",
      markerColor = ifelse(
        test = sch$number_of_reviews >= mean(sch$number_of_reviews,na.rm = TRUE), 
        yes = "blue",
        no = "green"
      )
    )
  ) %>%   # end addAwesomeMarkers()
  leaflet::addMeasure()
```

### Prix Moyen

```{r}
valueBoxSummaryWidget(
  summarywidget(
    sd,
    statistic = 'mean',
    column = 'price',
    digits = 0
  )
)

```


Column {data-width=350}
-------------------------------------
    
### Distrbution des Airbnb en foncton du Type d'habitation

```{r }

sd %>% 
plotly::plot_ly(y = ~room_type, type = "histogram",color =~room_type)%>%
  plotly::layout( yaxis=list(title="Type d'habitation"),showlegend = FALSE)


```

### Disbonibilité en nombre de jours par année

```{r }

sd %>% 
plotly::plot_ly(x = ~availability_365, type = "histogram",color =~room_type)%>%
  plotly::layout( xaxis=list(title="Nombre de jours"), legend = list(orientation = "v", xanchor = "center"))


```


### Nombre moyen de reviews

```{r}
valueBoxSummaryWidget(
  summarywidget(
    sd,
    statistic = 'mean',
    column = 'number_of_reviews',
    digits = 0
  ),
  color = "yellow"
)

```






Données
===================================== 

### Datatable
    
```{r datatable}
sd %>% 
  DT::datatable(
    filter = "top",  # allows filtering on each column
    extensions = c(
      "Buttons"
    ),
    rownames = FALSE,  # remove rownames
    style = "bootstrap",
    class = "compact",
    width = "100%",
    options = list(
      dom = "Blrtip",  # specify content (search box, etc)
      deferRender = TRUE,
      
      columnDefs = list(
        list(
          visible = FALSE,
          targets = c(2, 3, 5:15)
        )
      ), 
      buttons = list(
        I("colvis")
      )
    ),
    colnames = colnames(sch)
  )
```


